---
title: "Extract data from a Fitbit csv file"
author: "John Minter"
date: "Last updated: 2019-03-26"
output:
  rmarkdown::html_vignette:
    number_sections: true
    toc: true
    toc_depth: 2
vignette: >
  %\VignetteIndexEntry{Extract data from a Fitbit csv file}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


```{r, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE, comment=NA)
# suppressWarnings(suppressMessages(suppressPackageStartupMessages(library(dplyr))))
```
# Introduction

The interface for downloading data from Fitbit trackers has changed over the
years. Currently all of the R packages that use the Fitbit API are having
problems with authorization. I developed this package to scrape data from
very messy `.csv` files that can be downoaded from the website.

# Get the csv file

I added three csv files I downloaded as external data in the package.
We will use one of these.

```{r getCsvFile}

inF <- system.file("extdata", "2019-01.csv", package = "fitbitHelpR")
lines <- readLines(inF) 
length(lines)
```

Let's look at lines 1 to 5:

```{r l1to5, echo=FALSE}
for (i in seq(from=1, to=5)){
  print(lines[i])
}
```

Let's look at lines 34 to 40:

```{r l34to50, echo=FALSE}
for (i in seq(from=34, to=50)){
  print(lines[i])
}
```

and finally lines 67 to 72


```{r l67to72,echo=FALSE}

for (i in seq(from=67, to=72)){
  print(lines[i])
}

```

This is quite messy data...

# Process this messy data

I wrote the function `extract_fitbit_activity_data(csvFileName)`to do this.
It is **not pretty** but it works. Until they change the interface again...

```{r, message=FALSE}
library(fitbitHelpR)
tbl <- extract_fitbit_activity_data(inF)
tbl


```



